---
title: "Probable probabilities"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = here::here())

library(tidyverse)
library(patchwork)
library(extrafont)
loadfonts()

# To solve some conflicts between packages
select <- dplyr::select

# dplyr and ggplot settings
options(dplyr.summarise.inform = FALSE)
theme_set(theme_classic())
theme_update(text = element_text(family = "Fira Sans", size=12),
             axis.title.y = element_text(angle=0, vjust=0.5, hjust=0))

cbpalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
update_palette <- c("#ADE1FF", "#0072B2")  # prior, posterior
# update_palette <- c("#FFE09E", "#E69F00")  # prior, posterior
```


We have intuitions about how probable different probabilities of success are, given the data we observed.

We visualise them as a probability distribution:

```{r pstr-dens}
# The possible values for theta, the probability of success.
theta <- seq(0, 1, 0.001)

# Create the density function for 80 successes, 20 failures, over theta.
dens <- dbeta(theta, 80, 20)

tibble(
  theta = theta,
  dens = dens
) %>%
  ggplot(aes(x = theta, y = dens)) +
  # geom_density(fill = 'grey', alpha = 0.5, stat='identity') +
  geom_line(colour = update_palette[2]) +
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
  ) +
  labs(
    y = 'Probability\ndensity',
    x = 'Probability of answering correctly (theta)'
  ) +
  scale_x_continuous(breaks=seq(0, 1, 0.2)) +
  NULL
```

This is a **posterior** probability distribution, because it takes into account **information about the data,** as well as (implicitly, so far) information about **how probable we think each probability is to begin with.**

Let's make that implicit information explicit and see how we arrived at this posterior distribution step by step.

